\documentclass[10pt]{extarticle}
\usepackage{apMod}
% Licensed: https://www.gnu.org/licenses/gpl-3.0.html
% Template author: Anindya Prithvi
% define all your stuff here
\newcommand{\yourname}{Sameer Gupta}%
\newcommand{\youremail}{sameer21093@iiitd.ac.in}%
\newcommand{\youraddress}{Address: B-1/20, Mayur Vihar Phase-3, Delhi-110096}%
\newcommand{\yourrollno}{2021093}%
\newcommand{\yourDOB}{10 December, 2002}%
\newcommand{\yourgithub}{https://github.com/guptasameer112}
\newcommand{\yourphoto}{myphoto}% Only the filname without extension

\newcommand{\contain}{0}%1 if you make each section of your resume inseperable (try and see) This was added to deal with newpage within section

\begin{document}
\cvheader%
%
\begin{contained}
\sectionC{Education}
\begin{longtable}{p{0.8\textwidth}p{0.19\textwidth}p{0.01\textwidth}}
    \cveducationitem{Indraprastha Institute of Information Technology, Delhi}{B.Tech (CSE)}{2021 - present}{CGPA: 8.53\newline(Till 3\textsuperscript{rd} semester)}
    \cveducationitem{Somerville School, Vasundhara Enclave, Delhi}{CBSE, Standard 12, PCM+CS}{2020-2021}{Percentage : 94.4\%}
    \cveducationitem{Somerville School}{CBSE, Standard 10, PCM+CS}{2018-2019}{Percentage : 96\%}
\end{longtable}%
\vspace{0pt}
\end{contained}
%
\begin{contained}
\sectionC{Skills}
%nothing to modularize here, just write your stuff
\begin{longtable}{p{0.2\textwidth}p{0.75\textwidth}p{0.05\textwidth}}
    \textbf{Expertise Area:}&
    Data Structure \& Algorithm, Operating System, OOPs, Competitive Programming, Machine Learning, Database Management, \LaTeX \\
    \textbf{Programming \newline Languages:}&
    Java, Python, C++, C\\
    \textbf{Tools and\newline Technologies:}&
    Git, Github, Virtual Box, Django, React, IntelliJ IDEA, PyCharm, PyTorch, VSCode, Overleaf, Google Collab, Kaggle, Figma \\
    \textbf{Technical Electives:}&
    Algorithm Design \& Analysis, Data Structures \& Algorithms, Advanced Programming, Operating System, DBMS, Linear Algebra, Probability \& Statistics, Calculus, Discrete Mathematics.
\end{longtable}%
\vspace{0pt}
\end{contained}
%
\begin{contained}
\sectionC{Work Experience}
%nothing to modularize here, just write your stuff
\\
\begingroup%
\renewcommand\arraystretch{1}%
\begin{longtable}{p{0.8\textwidth}p{0.19\textwidth}p{0.01\textwidth}}
    \textbf{Undergraduate Researcher}&(Dec, 22 - Present)\\
    {Advisor: Dr. Sambuddho Chakravarty, Dr. Rinku Shah}\\
    To explore and identify the bottlenecks in firewall technologies and develop a faster firewall solution by leveraging hardware, stack, and application layer processing for efficient traffic handling.
    \\
    \textbf{Intern at TLE Eliminators}&(Jan, 23 - Present)\\
    Built the Feedback System for TLE Eliminators, a competitive coding learning platform led by Priyansh Agarwal.
\end{longtable}%
\endgroup%
\end{contained}
\vspace{0pt}
\begin{contained}
\sectionC{Projects}
% \vspace{-10pt}%
%nothing to modularize here, just write your stuff
%might add a row with \newline for techstack, but it seems pretty useless lol
\begin{longtable}{p{0.8\textwidth}p{0.19\textwidth}p{0.01\textwidth}}
    \textbf{Drug-Detection}\newline
    Using chEMBL dataset and RandomForestClassfier to predict pIC50 values of acetylcholinesterase enzyme.
    Repository \href{https://github.com/guptasameer112/Drug-Detection}{here}.
    &Team Size-1
    \newline (Jan, 23 - Feb, 23)\\
    \textbf{Potato-Diseases}\newline
    Using Keras and TensorFlow to create a potato disease detector. Repository \href{https://github.com/guptasameer112/Potato-Diseases}{here}.
    &Team Size-1
    \newline (Jan, 23)\\
    \textbf{Tank Stars - GUI Game}\newline
    A Clone of the popular Tank Stars Game, which focuses on tank fights. 
    Players are allowed to control the movements and attack trajectories.
    Repository \href{https://github.com/guptasameer112/Tank-Stars}{here}.
    &Team Size-2
    \newline (Aug, 22 - Dec, 22)\\
    \textbf{ASM-Assembler-Simulator}\newline
    Implemented a Custom Simulator and Assembler to convert assembly code to binary code (with error checks), and simulates the registers and execution.
 Repository \href{https://github.com/guptasameer112/Assembler-Simulator}{here}.
    &Team Size-2
    \newline (Jan, 21 - Apr, 21)\\
    \textbf{Market and News API}\newline
    For finance-related information, including news and prices, using Python3 and APIs. Done as the bonus project for the course Introduction to Programming (CSE101).
 Final report \href{https://github.com/guptasameer112/Market-and-News-API}{here}.
    &Team Size-3
    \newline (Jan, 22 - March, 22)\\
\end{longtable}
\end{contained}
\vspace{0pt}
\begin{contained}
\sectionC{Positions of Responsibility}
% \vspace{-10pt}
\begin{longtable}{p{0.8\textwidth}p{0.19\textwidth}p{0.01\textwidth}}
    IEEE Executive community Member & (Jan, 22 – Present)\\
    Content Writer \& Financial Analysis at Finnexia & (Jul, 22 - Present)\\
    Technical Head at D4rkc0de & (Jan, 22 - Present)\\
    Core Member at OWASP & (Jan, 22 - Dec, 22) \\
\end{longtable}
\vspace{0pt}
\end{contained}
\begin{contained}
\sectionC{Awards and Achievements}
\vspace{0pt}
\begin{itemize}
    \setlength\itemsep{0.5pt}
    \item \textbf{Flipkart GRid} 4.0 Level 2 Qualifier.
    \item Won the \textbf{Best Educational CTF Challenge Award} at DEF CON 30.
    \item Ranked \textbf{2nd WorldWide at WreckCTF 2022} as a member of d4rkc0de.
    \item Ranked \textbf{4th Worldwide at the Digital Overdose CTF 2022} as a member of d4rkc0de.
    \item Ranked \textbf{10th at the DEF CON Delhi 0x05 CTF} organised by DC911 group.
    \item \textbf{Won Aurora CTF} organised by DTU as a member of d4rkc0de.
\end{itemize}
\vspace{0pt}
\end{contained}
\sectionC{Interests and Hobbies}
\begin{contained}\\
\begin{itemize}
    \setlength\itemsep{0.5pt}
    \item Machine Learning 
    \item Finance
    \item Basketball
    \item Movies
    \item Music
\end{itemize}
% \vspace{5pt}
\end{contained}
Declaration: The above information is correct to the best of my knowledge.\newline
\yourname\newline
Date: \today
\end{document}